Basic concepts and tools for the Toki Pona minimalist language: Wordnet synsets; analysis, synthesis and syntax highlighting of texts

### 2017-12-01 article/article.tex
andando com stats

Given the rules given in Section~\ref{phonology}
(of 14 letters, 5 vowels, (C)V(N) phonemes,
forbidden ji, wu, wo, ti, nn, nm),
46 words are possible with 1 syllable,
1886 with 2 syllables, 77326 with 3 syllables.
No middle syllable end with the nasal consonant 'n'.
These are shown in Table~\ref{tab:pw}
with fraction of the space actually used in Toki Pona.

>>>>

Given the rules given in Section~\ref{phonology}
(of 14 letters, 5 vowels, (C)V(N) phonemes,
forbidden ji, wu, wo, ti, nn, nm),
96 words are possible with 1 syllable,
 96, 8256, 710016
8256 with 2 syllables, 710016 with 3 syllables.
No middle syllable end with the nasal consonant 'n'.
These are shown in Table~\ref{tab:pw}
with fraction of the space actually used in Toki Pona.
